% !TEX root = ../DoAn.tex
\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}

This thesis presents the complete analysis, design, and implementation of an e-commerce system
based on a microservices architecture, built with Spring Boot 3.5, Spring Cloud 2025, and Java 21.
The system is decomposed into 13 independent microservices following Domain-Driven Design (DDD)
and Bounded Context principles, each owning its own database and deployment lifecycle.

Service communication combines synchronous REST + OpenFeign with asynchronous Apache Kafka
(KRaft mode). Four core distributed patterns are fully applied: Saga Orchestration with
order-service acting as orchestrator for distributed transaction management; Transactional Outbox
guaranteeing at-least-once event publishing; Idempotent Consumer ensuring exactly-once processing
effect; and CQRS-lite with Elasticsearch as the read model for full-text search.

Two notable technical highlights are: (1) a flash sale over-sell prevention mechanism using
Redis Lua atomic scripts, buyer set, compensation, and reconciliation; (2) VNPAY payment gateway
integration with HMAC-SHA512 verification, Return URL, IPN callback handling, and timeout
scheduler. Security is centralized via Keycloak 26 (OAuth 2.0/OIDC) with JWT RS256, where
the API Gateway acts as Resource Server applying the Trusted Subsystem Pattern --- internal
services receive identity information via request headers without needing to call Keycloak on
every request.

In addition to the backend, the thesis implements a Next.js storefront and Admin Panel for
customer and administrator workflows. The system is packaged with Docker Compose and deployed
in a production-like single-host environment on AWS EC2, using Caddy for reverse proxy/HTTPS
and GitHub Actions/GHCR for image build and publishing. The observability stack includes
Prometheus, Grafana, and Zipkin, enabling metrics monitoring, distributed tracing, and
end-to-end debugging. Experimental results include 9/9 backend readiness suites passing,
k6 catalog/checkout/flash-sale tests, and resilience scenarios covering order-service, Kafka,
Redis, and inventory compensation.

\vspace{1cm}



\end{document}
